---
title: "Project 5"
author: "Philip Liman, Plim294"
subtitle: "Creating data from digital sources"
output: 
  html_document:
    code_folding: hide
date: "2024-05-22"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, message=FALSE, warning=FALSE, error=FALSE)
```

```{css echo=FALSE}
body { background-color: #FFDCDA; font-size: 15px; }

h2 { color: green; font-weight:700; font-size: 30px; font-family: "Lucida Console", "Courier New", monospace; border: 2px solid powderblue; }

h3 { color: maroon; font-family: Avirial, Helvetica, sans-serif; }
```

## Part A

[Github Website](https://philiplim1509.github.io/stats220/)

[Website Explore](https://www.worldometers.info/geography/how-many-countries-in-oceania/)

My data context is the countries in Ocenia. It gives the population and subregion of the countries in Oceania. 

I selected this data context because Oceania, as a geographical region, is where our home is. 
It also includes countries ranging from large land masses like Australia and Papua New Guinea to small island nations in the Pacific.
We can also do further exploration because it provides population and subregion (this might be usefull for grouping)

```{r file='partA.R'}

```
## Part B
```{r file='partB.R', results='hide'}

```

This is Hon Erica Stanford analysis of her released content:

The total number of words across all release contents is `r total_words`.

The average number of words per release is `r mean_words_per_release`.

The most common word in release titles is '`r most_common_title_word`' with a count of '`r title_word_counts[1]`'.

The most common word in release contents is '`r most_common_content_word`' with a count of '`r content_word_counts[1]`'.

## Part C
```{r file='partC.R'}

```

Immigration peaked at the year 2003, while crime and education peaked at the year 2006 (This was during the labour/progressive coalition and after their peak, all of the keywords number of speeches decrease over the year.)



## Learning reflection

One very important idea that I’ve learned from this course is data scraping. I had never used data scraping once in my entire time at university, so learning how to extract information from a website will definitely help with my major, which is BUSAN (they don’t even teach about data scraping). This also enhances my skills in data collection and pre-processing. Another key aspect is understanding where to scrape data from. Not all data is free to scrape due to legal, ethical, or technical reasons. It’s important to respect the terms of service of websites and to scrape responsibly.

Joins are also a valuable skill to learn because, in real life, not all data is going to be provided in one dataset. Most likely, we have to combine more than one, and joins are an effective way to combine datasets.

I want to learn more about advanced data scraping. For example, I could not scrape data that has interactive/hover elements in this assignment. I am also curious if we can bypass some of the robots.txt functions. If we could learn more about advanced data scraping and joins, I would be very interested.

## Self Review
The two skills I believe I have improved the most are data wrangling and visualization, and communication and reporting:

Using R, I have successfully learned how to import, clean, transform, and visualize data. The most notable skill is using code to manipulate the data (I usually use Excel for this). With R, I have gained a new skill set. Using ggplot is also helpful because it is very customizable, and there are many plots we can use. This relates back to Learning Outcome 2 (demonstrate programming concepts and skills...).

Another concept is communication and reporting. Without this course, I would have never used R Markdown to develop my reports or HTML and CSS for web-based reporting. Now, I am able to write dynamic reports using web technologies. This relates to Learning Outcome 4 (develop communication skills, using HTML...).

I want to include web scraping; however, we only briefly learned about it. I wish we could learn advanced techniques for it.

Overall, I have not only strengthened my technical skills in data wrangling and visualization but also improved my ability to effectively communicate and report my findings.